### 2014-02-22 paper/retrofit.tex
Fix reduction arrow.

\and
\inferrule[I-fork]
{ 
|iS' = iS [ id' mapsto nil ]|\\
|tS' = klone(tS)|\\
|fresh (id')|\\
|iTE' THole = iniTE (lconf id il tS id'), THole|
}
{|
iS, iniTE (lconf id il tS (fork ie))
.-.>
iS', iniTE' (lconf id' il tS' (TI ie))
|}
%{|fresh (id')|}

>>>>

\and
\inferrule[I-fork]
{ 
|iS' = iS [ id' mapsto nil ]|\\
|tS' = q(tS)|\\
|fresh (id')|\\
|iTE' THole = iniTE (lconf id il tS id'), THole|
}
{|
iS, iniTE (lconf id il tS (fork ie))
.-.>
iS', iniTE' (lconf id' il tS' (TI ie))
|}
%{|fresh (id')|}
